### 2012-12-10 counterexample to bratman on shared intention/a counterexample to bratman on shared intention.tex
in progress

\bibliographystyle{$HOME/Documents/submissions/mynewapa} %apalike

@@

\begin{abstract}
\noindent
The leading, best developed account of shared agency, Michael Bratman's, hinges on the claim that, roughly,
we have a shared intention if we each intend that we J and also that we J by way of these intentions and meshing subplans of them where this is all common knowledge.
This paper provides a counterexample to the sufficiency of this condition for shared intention.
The counterexample arises because it is possible for agents to meet the condition, and to act rationally on the specified  intentions and knowledge,
 while conceiving of each other's actions only as constraints to work around and opportunities to exploit.
Shared agency requires more than this, or so we argue.
We also suggest a way of revising Bratman's account  that is consistent with his general approach.
In some or all cases, shared agency differs from individual agency in part because shared agency involves changing perspective so that one’s own and other’s actions are conceived of as parts of a single plan.

@@

How else could we support the claim that Beatrice and Baldric lack a shared intention? 
As mentioned at the start, 
the contrast cases are often used to anchor intuitions in theorising about shared agency.
In the next section we shall further support our claim by contrasting Beatrice and Baldric's case with a further case, one which is as similar as possible and which does seem to involve shared agency.
The fact that Beatrice and Baldric's case contrasts with this new case will support the claim that Beatrice and Baldric lack shared intention.
This is the aim of the following section.
A further motive for introducing this new contrast case is that it provides an indication concerning what is missing from Bratman's account, and so may help us to understand why his conditions are not sufficient for shared intention.

@@

Above we introduced what will turn out to be a counterexample to Bratman's account, the case of Beatrice and Baldric. 
But we have yet to show that this case really is a counterexample. 
For all we have said so far, a proponent of Bratman's view might insist that Beatrice and Baldric do have a shared intention that they J$_1$.
To show that they do not,
we shall contrast Beatrice and Baldric's case with a third case that is as similar as possible but does involve shared intention.

@@

First we need to introduce the notion of an agent-neutral plan and some  observations.
We stipulate that a planning process, or a plan, is \emph{agent-neutral} just if it does not involve identifying any particular agents.  
This sort of planning is quite common.
For example, some housemates who have decided to make a pizza might sit down together to plan what needs doing without yet assigning roles to particular individuals. 
Someone needs to prepare the dough, 
another person should prepare toppings,
while a third might mix some salad.
In so planning, each housemate is thinking about what is to be done and not what she herself will do.  
%(This is an idealisation, of course.)
At some point the housemates stop planning.
(This does not necessarily mean that they have a fully worked out plan; like any other plans, agent-neutral plans can have gaps that may need filling in later.)
They now divide up the roles.
Of course they may not find a way of dividing up roles that everyone is prepared to go along with---individuals' preferences, abilities and intentions may block the plan's adoption.
But suppose the housemates do divide up the roles in a way that is acceptable to everyone, 
	and that each implements her part in the plan.
Then each conceives of her own and the others' actions as part of single plan directed to achieving a single outcome.

@@

If some agents each individually plan all of the agents' actions, 
could they nevertheless know  that they will form plans that are sufficiently similar or jointly viable?%
\footnote{
\label{fn:df_jointly_viable}
Suppose that, for some outcome, two or more agents each have a plan for the realisation of that outcome. 
%(These plans may, but need not, specify roles for all of the agents; but the plans must be agent-specific, not agent-neutral.)
We stipulate that these plans are  \emph{jointly viable} just if
the plan which involves each agent performing the roles she is assigned in her own plan is acceptable to all the agents and a viable means of realising the outcome.
For an example of jointly viable but significantly different plans, suppose that our task is to transport some apples and pears to a warehouse. 
My plan involves you taking care of the apples while I put the pears into the yellow crates and load them into the van through the side door.
If your plan involves me taking care of the pears while you put the apples into the green crates and load them into the van through the rear doors, then our plans are compatible.
Consider also a case in which our task is to press a button simultaneously. 
If your plan is that each of us will to start to act in exactly 60 seconds whereas my plan specifies that you are the leader and we will start to act when you do, then our plans are jointly viable.
}
%Where the agents could bring about an outcome in several different, equally good ways,
%having some agents each individually plan all of the agents' actions is probably not useful.
Consider housemates
	making a pizza together, where everyone knows roughly the same recipe and differences are unlikely to matter.
Or consider two agents 
 moving  a table from one room to another together, where there is an obviously optimal route and the agents' positions manifestly determine which ends of the tables they should hold.
For these outcomes and situations,
 the agents' expertise and planning strategies 
 may mean that each could knowledgeably predict that they will form sufficiently similar agent-neutral plans.
And sometimes commonly known properties of the agents, such as their distribution in space or their sizes, mean that there is exactly one most obvious way of dividing up roles.
%If  each agent also  knows enough about herself and the others to be able to determine, without communicating, whether her plan and role assignments will be acceptable to everyone, then
% it need not be irrational for the agents each individually to plan all of the agents' actions. 
In any such case, the agents who each individually plan all of the agents' actions may form sufficiently similar plans and know that they will do so.

Agents who will collaborate in some way, such as by making a pizza together, can coordinate their actions by each individually planning all of the agents' actions.
Suppose some agents 
	 are about to act together in order to bring about some outcome.
They know (we stipulate) that if they each individually plan all of the agents' actions, they will form sufficiently similar plans.
Each agent also knows enough about herself and the others to be able to determine, without communicating, that the resulting plans will be acceptable to everyone. 
And all of this is common knowledge to the agents.  
Then these agents 
might individually plan all of the agents' actions,
and each might rationally perform her part in her plan, knowing that the others will do likewise.
In this way, 
 some agents' individually planning all of the agents' actions can rationally coordinate their plans and actions.%
\footnote{
Note that this coordination is achieved without presupposing that the agents exercise shared agency.
Of course,
	if some agents individually plan all of the agents' actions
	and then each rationally performs her part in her own plan,
	the upshot might be an exercise of shared agency.
But this shared agency is a consequence of, not a requirement on, their individually planning all of the agents' actions.
}

But why would some agents each individually plan all of the agents' actions?
After all, no agent gets  to perform  others' actions
(or, if they do, this is exceptional).
So why would anyone individually plan others' actions, knowing that she won't perform them?
In many cases, 
a plan for one agent's actions would need to be constrained by, and to constrain, plans for other agents' actions.
When, for example,
two people are about to move a heavy table from one room to the next,
two separate plans for their individual actions would have to involve compatible timings, forces and routes.
In principle,  each table-lifter might form an initial plan for her own actions only.
Each could use her initial plan to make predictions about the  other's likely actions.
She could then revise the plan for her own actions in the light of these predictions.
This cycle of prediction and revision might be repeated.
The plans might also involve conditional elements to accommodate unpredicted actions.
So when an agent plans only her own actions,
 she will sometimes need to rely on predictions about what others will do,
 and these predictions will sometimes depend on what the agent plans to do.
Another 
 way to proceed
	would be for the agent to plan all of the agents' actions,
perhaps by first making an agent-neutral plan and then assigning roles.
So the reason why some agents might each plan all of the agents' actions is that doing so provides one way to solve a coordination problem.
We don't claim that this is the only or best way to coordinate.
Our claim is just that some agents sometimes achieve coordination in part by means of each agent's individually planning all of the agents' actions.%
\footnote{
As an aside, we note that 
\citet{tsai:2011_groop_effect} provide evidence indicating that planning for one's own and and others' actions happens not only in conscious practical reasoning but also in planning that we may not ordinarily be directly aware of.
}

Now recall Beatrice and Baldric (from Section \vref{sec:the_counterexample}).
We said earlier that  they each see the other's actions  as constraints to work around or opportunities to exploit only.
This is because each agent plans only her own actions.
Neither agent plans for both of their actions and so neither conceives of both of their actions as parts of a single plan.
In constructing a case that contrasts with Beatrice and Baldric's we shall rely on the distinction between
a plan that includes both one's own and others' actions
and 
a plan that merely exploits, and is constrained by, predictions about the others' actions.
This distinction matters independently of whether two such plans would result in different actions.
It matters because 
forming a plan for your own and others' actions 
	involves changing perspective.
That is, it involves conceiving of the others' actions not only as constraints and opportunities, but as on a par with your own actions insofar as your actions and theirs are elements in a single plan directed to a single outcome.

In the case of ordinary, individual agency,
there is a familiar and  important distinction between merely predicting one's own actions and planning them.%
%
\footnote{
Even Velleman, who argues that `[d]eciding on an action … is just a peculiar way of predicting it' (\citeyear[p.\ 48]{Velleman:1985mc}), can accommodate a distinction between merely predicting and planning actions \citep[see][p.\ 195]{Velleman:2000fq}.
%“How can one regard a proposition as true in such a way as to make it true? Well, when one accepts a proposition in response to its truth, one registers the influence of evidence and other reasons for belief, thereby manifesting an incli-nation to conform one’s acceptance to the facts. Accepting a proposition in such a way as to make it true would simply require a converse inclination, to conform the facts to one’s acceptance. And one can indeed be inclined to conform the facts to one’s acceptance, if the proposition accepted is about one’s own behavior. One need only be inclined to do what one accepts that one will do. If one has this inclination, then accepting that one will do something can be a way of making this proposition true, and it can therefore be an attempt at accepting the truth.”  (195)
}
%
It is possible and perhaps sometimes useful to make predictions about one's future actions, of course.
But to rely on predictions about one's own actions in planning can involve a kind of estrangement from oneself \citep[compare][]{Moran:2001hr}.
We have just been arguing that 
in the case of shared agency,
the distinction between predicting and planning actions also applies to the actions of agents other than oneself.

Applying this distinction in cases of shared agency requires additional subtlety, of course.
After all,
one agent cannot rationally include another's actions in a plan she knows she will act on unless she could predict the other's actions.
(Or unless she knows the other agent will act directly on the first's intentions---see \citet{roth_shared_agency}.) 
This fact should not obscure the distinct ways in which one conceives of another agent's actions in planning and predicting them, however.
For, as we have argued, in some cases planning another agent's actions does not require actually predicting them.
In some cases, planning another's actions does not depend on having predicted them but rather provides a ground for prediction.
This is why there is a difference in perspective between merely predicting another's actions and conceiving of them as on a par with one's own in being elements of a single plan.

Now that we have some background on how some agents might each individually plan all of the agents' actions,
we can introduce a third and final case.
This case needs to be as similar as possible to Beatrice and Baldric's while involving shared agency.

@@

We stipulate that an activity is \emph{distributed} just if: 
\begin{enumerate}[label=\emph{\alph*})]
\item 	there is a single outcome, G,
	and two or more agents each have a plan for G which specifies a role for all of the agents;	
\item 	these plans are identical or compatible,%
\footnote{
The notion of compatibility is defined in footnote \vref{fn:df_compatible}.
}
%
		and they are each acceptable to all; 
\item	each agent performs the roles assigned to her in her own plan;
\item	the activity consists in nothing other than the agents performing these roles;
	and
\item	by performing these roles, the agents G.

@@

Distributed activities can be simple.
In walking to a metro station together,
two friends may each form and act on a plan that specifies some details of both of their actions.
This is enough for their activity to be distributed in the above sense.

@@

No amount of forming intentions about other's intentions and acting on knowledge of such intentions is sufficient, all by itself, for shared intention.  
In many or all cases, shared agency requires changing perspective 
to conceive of one's own and others' intentions and actions as parts of a single plan.

>>>>

%screws up word count for some reason:
\bibliographystyle{$HOME/Documents/submissions/mynewapa} %apalike

@@

\begin{abstract}
\noindent
The leading, best developed account of shared agency, Michael Bratman's, hinges on the claim that, roughly,
we have a shared intention if we each intend that we J and also that we J by way of these intentions and meshing subplans of them where this is all common knowledge.
This paper provides a counterexample to the sufficiency of this condition for shared intention.
The counterexample arises because it is possible for agents to meet the condition, and to act rationally on the specified  intentions and knowledge,
 while conceiving of each other's actions only as constraints to work around and opportunities to exploit.
Shared agency requires more than this, or so we argue.
We also suggest a way of revising Bratman's account  that is consistent with his general approach.
In some or all cases, shared agency differs from individual agency in part because shared agency involves 
changing perspective 
to conceive of your own and another's actions  as parts of a single plan.

@@

How else could we support the claim that Beatrice and Baldric lack a shared intention? 
As mentioned at the start, 
the contrast cases are often used to anchor intuitions in theorising about shared agency.
In the next sections we shall further support our claim by contrasting Beatrice and Baldric's case with a further case, one which is as similar as possible and which does seem to involve shared agency.
The fact that Beatrice and Baldric's case contrasts with this new case will support the claim that Beatrice and Baldric lack shared intention.
This is the aim of the following sections.
A further motive for introducing this new contrast case is that it provides an indication concerning what is missing from Bratman's account, and so may help us to understand why his conditions are not sufficient for shared intention.

@@

Above we introduced what will turn out to be a counterexample to Bratman's account, the case of Beatrice and Baldric. 
But we have yet to show that this case really is a counterexample. 
For all we have said so far, a proponent of Bratman's view might insist that Beatrice and Baldric do have a shared intention that they J$_1$.
To show that they do not,
we shall contrast Beatrice and Baldric's case with a third case that is as similar as possible but does involve shared intention (see Section \vref{sec:new_contrast_case}). 
Before introducing this third case,
we first need to introduce the notion of an agent-neutral plan and some background on planning.

@@

We stipulate that a planning process, or a plan, is \emph{agent-neutral} just if it does not involve identifying any particular agents.  
This sort of planning is quite common.
For example, some housemates who have decided to make a pizza might sit down together to plan what needs doing without yet assigning roles to particular individuals. 
Someone needs to prepare the dough, 
another person should prepare toppings,
while a third might mix some salad.
In so planning, each housemate is thinking about what is to be done and not what she herself will do.  
%(This is an idealisation, of course.)
At some point the housemates stop planning.
(This does not necessarily mean that they have a fully worked out plan; like any other plans, agent-neutral plans can have gaps that may need filling in later.)
They now divide up the roles.
Of course they may not find a way of dividing up roles that everyone is prepared to go along with---individuals' preferences, abilities and intentions may block the plan's adoption.
But suppose the housemates do divide up the roles in a way that is acceptable to everyone, 
	and that each implements her part in the plan.
Then each conceives of her own and the others' actions as part of single plan directed to achieving a single outcome.

@@

If some agents each individually plan all of the agents' actions, 
could they nevertheless know  that their various plans will be  sufficiently similar or jointly viable?%
\footnote{
\label{fn:df_jointly_viable}
Suppose that, for some outcome, two or more agents each have a plan for the realisation of that outcome. 
%(These plans may, but need not, specify roles for all of the agents; but the plans must be agent-specific, not agent-neutral.)
We stipulate that these plans are  \emph{jointly viable} just if
the plan which involves each agent performing the roles she is assigned in her own plan is acceptable to all the agents and a viable means of realising the outcome.
For an example of jointly viable but significantly different plans, suppose that our task is to transport some apples and pears to a warehouse. 
My plan involves you taking care of the apples while I put the pears into the yellow crates and load them into the van through the side door.
If your plan involves me taking care of the pears while you put the apples into the green crates and load them into the van through the rear doors, then our plans are compatible.
Consider also a case in which our task is to press a button simultaneously. 
If your plan is that each of us will to start to act in exactly 60 seconds whereas my plan specifies that you are the leader and we will start to act when you do, then our plans are jointly viable.
}
%Where the agents could bring about an outcome in several different, equally good ways,
%having some agents each individually plan all of the agents' actions is probably not useful.
Consider housemates
	making a pizza together, where everyone knows roughly the same recipe and differences are unlikely to matter.
Or consider two agents 
 moving  a table from one room to another together, where there is an obviously optimal route and the agents' positions manifestly determine which ends of the tables they should hold.
For these outcomes and situations,
 the agents' expertise and planning strategies 
 may mean that each could knowledgeably predict that they will make sufficiently similar agent-neutral plans.
And sometimes commonly known properties of the agents, such as their distribution in space or their sizes, mean that there is exactly one most obvious way of dividing up roles.
%If  each agent also  knows enough about herself and the others to be able to determine, without communicating, whether her plan and role assignments will be acceptable to everyone, then
% it need not be irrational for the agents each individually to plan all of the agents' actions. 
In any such case, the agents who each individually plan all of the agents' actions may end up with sufficiently similar plans and know that they will do so.

Agents who will collaborate in some way, such as by making a pizza together, can coordinate their actions by each individually planning all of the agents' actions.
Suppose some agents 
	 are about to act together in order to bring about some outcome.
They know (we stipulate) that if they each individually plan all of the agents' actions, they will end up with sufficiently similar plans.
Each agent also knows enough about herself and the others to be able to determine, without communicating, that the resulting plans will be acceptable to everyone. 
And all of this is common knowledge to the agents.  
Then these agents 
might individually plan all of the agents' actions,
and each might rationally perform her part in her plan, knowing that the others will do likewise.
In this way, 
 some agents' individually planning all of the agents' actions can rationally coordinate their plans and actions.%
\footnote{
Note that this coordination is achieved without presupposing that the agents exercise shared agency.
Of course,
	if some agents individually plan all of the agents' actions
	and then each rationally performs her part in her own plan,
	the upshot might be an exercise of shared agency.
But this shared agency is a consequence of, not a requirement on, their individually planning all of the agents' actions.
}

But why would some agents each individually plan all of the agents' actions?
After all, no agent gets  to perform  others' actions
(or, if they do, this is exceptional).
So why would anyone individually plan others' actions, knowing that she won't perform them?
In many cases, 
a plan for one agent's actions would need to be constrained by, and to constrain, plans for other agents' actions.
When, for example,
two people are about to move a heavy table from one room to the next,
two separate plans for their individual actions would have to involve compatible timings, forces and routes.
In principle,  each table-lifter might make an initial plan for her own actions only.
Each could use her initial plan to make predictions about the  other's likely actions.
She could then revise the plan for her own actions in the light of these predictions.
This cycle of prediction and revision might be repeated.
The plans might also involve conditional elements to accommodate unpredicted actions.
So when an agent plans only her own actions,
 she will sometimes need to rely on predictions about what others will do,
 and these predictions will sometimes depend on what the agent plans to do.
Another 
 way to proceed
	would be for the agent to plan all of the agents' actions,
perhaps by first making an agent-neutral plan and then assigning roles.
So the reason why some agents might each plan all of the agents' actions is that doing so provides one way to solve a coordination problem.
We don't claim that this is the only or best way to coordinate.
Our claim is just that some agents sometimes achieve coordination in part by means of each agent's individually planning all of the agents' actions.%
\footnote{
As an aside, we note that 
\citet{tsai:2011_groop_effect} provide evidence indicating that planning for your own and and others' actions happens not only in conscious practical reasoning but also in planning that you may not ordinarily be directly aware of.
}

Now recall Beatrice and Baldric (from Section \vref{sec:the_counterexample}).
We said earlier that  they each see the other's intentions and actions  as constraints to work around or opportunities to exploit only.
This is because neither agent plans all of their actions and so neither conceives of both her own and the other's actions as parts of a single plan.
In constructing a case that contrasts with Beatrice and Baldric's we shall rely on the distinction between
a plan that includes both your own and another's actions
and 
a plan that merely exploits, and is constrained by, predictions about the other's actions.
This distinction matters independently of whether two such plans would result in different actions.
It matters because 
making a plan for your own and another's actions 
	involves changing perspective.
That is, it involves conceiving of the other's actions not only as constraints and opportunities, but as on a par with your own actions insofar as your actions and their actions are elements in a single plan directed to a single outcome.

Note that our key distinction is not between merely predicting and planning another agent's actions.
Beatrice and Baldric each intend to make the cross hit the red square (that is, to J${_1}$) in accordance with, and in part because of, each other's intentions.
So when Beatrice predicts what Baldric will do, she can rely on facts about his intentions.
She may even make predictions by planning his actions,
and Baldric may likewise predict Beatrice's actions by planning them.
So we can suppose that each plans the other's actions as well as separately planning her own actions,
and that these two planning activities constrain each other.
But---and this is our key distinction---neither makes a single plan for both her own and the other's actions.

\section{One Plan or Two?}
The distinction between making a single plan and making two separate plans may initially seem too subtle to be useful, 
especially as 
the two separate plans may be interdependent.
Further, if two separate plans could both be executed (not just each plan but both together), then they can be combined into a single plan.
The combined plan is simply to implement each of the two formerly separate plans. 
Given these apparent grounds for scepticism,
in this section we shall explain why the distinction between making a single plan and making two separate plans matters.

***First,
the fact that two separate \emph{plans} can be combined doesn't undermine the distinction between \emph{making} a single plan and \emph{making} two separate plans.
To see why consider structure ...
[... but the really deep point is not about structure: it's about keeping plans separate meaning adopting a predictive rather than a deliberative perspective towards the actions ...]

Let us step back from shared agency  
 to consider how 
 the distinction between making a single plan and making two separate plans
  applies in cases of ordinary, individual agency.
Suppose you have to organise two events, a workshop and a wedding.
If the two events were largely independent of each other,
it would be simplest to make two separate plans for them.
But in this case there are all kinds of constraints linking the two events.
Some participants at the workshop are also wedding guests,
and it happens that many choices of transport, entertainment and catering for one event constrain possible choices for the other event.
In principle you could handle these by making two separate plans where, at any stage of your planning, making one plan involves treating the other plan as providing constraints to work around and opportunities to exploit.
But envisaging the complex interdependence of these two plans  
might reasonably incline you to make a single plan for the wedding and workshop.
Making a single plan can be simpler because it allows for structuring the requirements differently.
For instance, if you have two separate plans, you will need subplans for transport in each plan and so are forced to divide the problem of transporting participants into the problem of transporting them for the workshop and the problem of transporting them for the wedding.
Having a single plan for both events allows you to treat transport as a single problem (but it does not require you to do so, of course).
As this indicates, the distinction between making a single plan and making two separate but interdependent plans is not merely notional.
Agents can have reasons for making a single plan rather than two separate ones.

This claim needs qualification, however.
It might be held that single agents always combine all plans for their own actions ... unity of their plans ... leads to the Moran point ***

There is a familiar and  important distinction between merely predicting your own actions and planning them.%
%
\footnote{
Even Velleman, who argues that `[d]eciding on an action … is just a peculiar way of predicting it' (\citeyear[p.\ 48]{Velleman:1985mc}), can accommodate a distinction between merely predicting and planning actions.
In his terms, we might say that 
planning involves not merely predicting but also being inclined to make the prediction true \citep[see][p.\ 195]{Velleman:2000fq}.
%“How can one regard a proposition as true in such a way as to make it true? Well, when one accepts a proposition in response to its truth, one registers the influence of evidence and other reasons for belief, thereby manifesting an inclination to conform one’s acceptance to the facts. Accepting a proposition in such a way as to make it true would simply require a converse inclination, to conform the facts to one’s acceptance. And one can indeed be inclined to conform the facts to one’s acceptance, if the proposition accepted is about one’s own behavior. One need only be inclined to do what one accepts that one will do. If one has this inclination, then accepting that one will do something can be a way of making this proposition true, and it can therefore be an attempt at accepting the truth.”  (195)
}
%
It is possible and perhaps sometimes useful to make predictions about your future actions, of course.
%*nb 'your ... oneself' issue in this sentence:
But to rely on mere predictions about your own actions in planning can involve a kind of estrangement from oneself \citep[compare][]{Moran:2001hr}.

We are arguing that 
something similar applies in the case of shared agency, 
except that here the distinction between predicting and planning actions also applies to others' actions.

Applying this distinction in cases of shared agency requires additional subtlety, of course.
After all,
you cannot rationally include another's actions in a plan you know you will act on unless you could predict the other's actions.%
%
\footnote{
This statement requires qualification if, as \citet{roth_shared_agency} argues, 
another agent might act directly on your intentions. 
As the cases we are considering involve agents in symmetric roles, we can ignore that possibility here.
We acknowledge, however, that Roth's idea has inspired the less radical view defended in this section.
}
%
This fact should not obscure the distinct ways in which one conceives of another agent's actions in planning and predicting them, however.
For, as we have argued, in some cases planning another agent's actions does not require actually predicting them.
In some cases, planning another's actions does not depend on having predicted them but rather provides a ground for prediction.
This is why 
different perspectives are involved in 
	merely predicting another's actions 
	and 
	conceiving of her actions and  your own actions as elements of a single plan.

\section{A New Contrast Case}
\label{sec:new_contrast_case}
Now that we have some background on how some agents might each individually plan all of the agents' actions,
we can introduce a third and final case.
This case needs to be as similar as possible to Beatrice and Baldric's while involving shared agency.

@@

We stipulate that an activity is \emph{distributed} just if: 
\begin{enumerate}[label=\emph{\alph*})]
\item 	there is a single outcome, G,
	and two or more agents each have a plan for G which specifies  roles for all of the agents;	
\item 	these plans are identical or compatible,%
\footnote{
The notion of compatibility is defined in footnote \vref{fn:df_compatible}.
}
%
		and they are each acceptable to all; 
\item	each agent performs the roles assigned to her in her own plan;
\item	the activity consists in nothing other than the agents performing these roles;
	and
\item	by performing these roles, the agents G.

@@

Distributed activities can be simple.
In walking to a metro station together,
two friends may each make and act on a plan that specifies some details of both of their actions.
This is enough for their activity to be distributed in the above sense.

@@

No amount of forming intentions about other's intentions and acting on knowledge of such intentions is sufficient, all by itself, for shared intention.  
In many or all cases, shared agency requires changing perspective 
to conceive of your own and another's intentions and actions as parts of a single plan.
